\section{List of abbreviations}
\textbf{AMCT}: chemotherapy given in the adjuvant or metastatic setting, \textbf{AOCS}: Australian Ovarian Cancer Study, \textbf{COSMIC}: the Catalogue Of Somatic Mutations In Cancer, \textbf{MNV}: multi nucleotide variant, \textbf{NACT}: neoadjuvant chemotherapy, \textbf{SNV}: single nucleotide variant

\section{Ethics approval and consent to participate}
The AOCS obtained ethics board approval at all institutions for patient recruitment, sample collection and research studies. Written informed consent was obtained from all participants in this study.

\section{Consent for publication}
Not applicable.

\section{Availability of data and materials}
All data generated during this study are included in this published article and its supplementary information files.

\section{Competing interests}
The authors declare that they have no competing interests.

\section{Funding}
This research was supported by the Marsha Rivkin Foundation and NIH/NCI Cancer Center Support Grant P30 CA008748.

\section{Authors' contributions}
TO, DB, AS, and JH conceived and coordinated the study. TO performed the research and wrote the manuscript. EC curated the clinical records. JN and BAA advised on analysis methods.  All authors revised the manuscript critically.

\section{Acknowledgements}
We thank Leonid Rozenberg for assistance with sequence-based HLA typing and Arun Ahuja for help running the analyses. We also thank Dariush Etemadmoghadam and Ann-Marie Patch at Peter MacCallum Cancer Centre for assistance accessing Australian Ovarian Cancer Study sequencing and clinical data.
