\section*{Background}

Several chemotherapies including platinum compounds~\cite{Hannan_1989}, cyclophosphamide~\cite{Anderson_1995}, and etoposide~\cite{NAKANOMYO_1986} exert their effect through DNA damage, and recent studies have found evidence for chemotherapy-induced mutations in post-treatment acute myeloid leukaemia~\cite{Ding_2012}, glioma~\cite{Johnson_2013}, and esophageal adenocarcinoma~\cite{Murugaesu_2015}. With the development of immune checkpoint-mediated therapy\cite{Chen_2013}, there is increasing appreciation for the importance of T cell neoantigens arising from somatic mutations in anti-tumor immune responses~\cite{Schumacher_2015}. Studies based on bulk-sequencing of tumor samples followed by computational peptide-class I MHC affinity prediction have suggested that tumors with more mutations and potential mutant MHC peptide ligands, which we refer to as neoantigens, may be more likely to respond to checkpoint blockade immunotherapy~\cite{Van_Allen_2015,Rizvi_2015}. It has therefore been suggested that the relatively low neoantigen burden in ovarian cancer may explain the limited effectiveness of certain immunotherapies in this disease~\cite{Martin_2016}. However, the effect of standard adjuvant and neoadjuvant chemotherapy regimes on detectable tumor mutations and resulting neoantigens is unknown.

% Several chemotherapies including platinum compounds~\cite{Hannan_1989}, cyclophosphamide~\cite{Anderson_1995}, and etoposide~\cite{NAKANOMYO_1986} have long been known to be mutagenic, and recent studies have found evidence for chemotherapy-induced mutations in post-treatment acute myeloid leukaemia~\cite{Ding_2012}, glioma~\cite{Johnson_2013}, and esophageal adenocarcinoma~\cite{Murugaesu_2015}. At the same time, there is increasing appreciation for the importance of T cell neoantigens arising from somatic mutations in anti-tumor immune responses~\cite{Schumacher_2015}. Patients whose tumors harbor more neoantigens may have better prognosis~\cite{Brown_2014} and are more likely to respond to checkpoint blockade immunotherapy~\cite{Van_Allen_2015,Rizvi_2015}. It has been suggested that a relatively low neoantigen burden in ovarian cancer may explain the limited effectiveness of certain immunotherapies in this disease~\cite{Martin_2016}, raising the question if chemotherapy might be used specifically to increase neoantigen burden. However, the effect of standard chemotherapy regimes on tumor mutations and resulting neoantigens in both the neoadjuvant and adjuvant settings is unknown.

Investigators associated with the Australian Ovarian Cancer Study (AOCS) performed whole genome and RNA sequencing on 114 cancer samples from 92 patients with high grade serous ovarian carcinoma~\cite{Patch_2015}. Seventy-nine samples were taken before chemotherapy, 30 after adjuvant chemotherapy, and 5 after neoadjuvant therapy. Treatment regimes varied but always included platinum-based chemotherapy. In their primary analysis, Patch et al. reported that post-treatment samples harbored more somatic mutations than pre-treatment samples and exhibited evidence of chemotherapy-associated mutations. Here we extend these results by quantifying the mutations and predicted neoantigens attributable to chemotherapy-associated mutational signatures.

Because the AOCS patients received adjuvant chemotherapy, it isn't possible to distinguish chemotherapy-induced mutations from temporal effects when comparing primary and relapse samples by mutation count alone. Recently, discrete mutational patterns, known as signatures, in melanoma, breast, lung and other cancers have been associated with exposure to particular mutagens, age related DNA changes, and disruption of DNA damage repair pathways due to somatic mutations or germline risk variants~\cite{Alexandrov2013}. Mutagenic signatures therefore provide a means of identifying the contribution that chemotherapy may make to the mutational changes seen in relapse samples. For example, the chemotherapy temozolomide has been shown to induce mutations consisting predominantly of $C \rightarrow T$ (equivalently, $G \rightarrow A$) transitions at CpC and CpT dinucleotides~\cite{Johnson_2013}. To perform deconvolution, the SNVs observed in a sample are evaluated in their trinucleotide contexts, and a combination of signatures, each corresponding to a mutagenic process, is found that best explains the observed counts. Mutational signatures may be discovered \textit{de novo} from large cancer sequencing projects, but for smaller studies it is preferable to deconvolve into known signatures~\cite{Rosenthal_2016}, as we do here.

% As paclitaxel/carboplatin therapy following surgery is standard of care, all AOCS relapse samples were exposed to chemotherapy. Therefore, the effect of chemotherapy on mutational burden cannot be statistically separated from those of drift and relapse in this cohort. Mutational signature deconvolution provides an alternative by incorporating outside information on the trinucleotide sequence context biases of particular mutagenic processes. For example, mutations arising due to disruption of mismatch repair have a high number of C to T mutations where the 5' and 3' adjacent bases are both G. To perform deconvolution, the SNVs observed in a sample are counted by trinucleotide context, and a combination of signatures, each corresponding to a mutagenic process, is found that best explains the observed counts~\cite{Alexandrov2013}. Mutational signatures may be discovered \textit{de novo} from large cancer sequencing projects, but for smaller studies it is preferable to deconvolve into known signatures~\cite{Rosenthal_2016}, as we do here.

The COSMIC Signature Resource curates 30 signatures from pan-cancer analyses. While signatures for chemotherapy exposure have not been established from human studies, two recent reports provide data on mutations detected in chemotherapy-exposed \textit{C. Elegans} organisms~\cite{Meier_2014} and a \textit{G. Gallus} (chicken) cell line~\cite{Szikriszt_2016}. The \textit{C. Elegans} study considered cisplatin and other compounds across a range of DNA repair-deficient knockout models. The \textit{G. Gallus} study examined a number of chemotherapies, including cisplatin, cyclophosphamide, and etoposide, in wildtype \textit{G. Gallus} cell lines. Based on the mutations identified in these studies, we extracted two signatures for cisplatin, a signature for cyclophosphamide, and a signature for etoposide. We performed signature deconvolution on the AOCS dataset using these four chemotherapy signatures plus the 30 COSMIC signatures and estimated the neoantigens attributable to each signature.

% The COSMIC Signature Resource curates 30 signatures from pan-cancer analyses; a number of these have known associations with mutagenic processes such as disruption of mismatch repair pathways or ultraviolet light exposure~\cite{364242}. While signatures for chemotherapy exposure have not been established from human studies, two recent reports provide data on mutations detected in chemotherapy-exposed \textit{C. Elegans} organisms~\cite{Meier_2014} and a \textit{G. Gallus} (chicken) cell line~\cite{Szikriszt_2016}. The \textit{C. Elegans} study considered cisplatin and other compounds across a range of DNA repair-deficient knockout models. The second study examined a number of chemotherapies, including cisplatin, cyclophosphamide, and etoposide, in wildtype \textit{G. Gallus} cell lines. Based on the mutations identified in these studies, we extracted 10 signatures for cisplatin in various genetic contexts, 1 signature for cyclophosphamide, and 1 signature for etoposide. We then performed signature deconvolution on the AOCS dataset using these the chemotherapy signatures plus the 30 COSMIC signatures.

% Given these results, we wondered if this dataset could be used to assess the effect of chemotherapy on mutation and neoantigen burden.
% analysis might be extended to quantify the number of neo whether chemotherapy leads to more neoantigens.


